Supplementary Figures

### 2024-04-29 supplementary_plots.Rmd
update paths

# Open dataset-------------
# start with lake temperatures
temperature_scores <- arrow::open_dataset("./scores") |>
  dplyr::filter(!(model_id %in% c('flareGOTM','flareGOTM_noDA', 'flare_ler', 'flare_ler_baseline') &
                  site_id == 'TOOK')) |> 
  filter(site_id %in% lake_sites,
         model_id %in% model_meta$model_id,
         variable == 'temperature') |>
  collect()

>>>>

# Open dataset-------------
# start with lake temperatures
temperature_scores <- arrow::open_dataset("./scores") |> 
  filter(site_id %in% lake_sites,
         model_id %in% model_meta$model_id,
         variable == 'temperature') |>
  collect()
